### 2021-10-01 analysis/fit_models.Rmd
made individual plots. need combining for chapter 1 in gimp.

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(ggplot2)
theme_set(
  theme_classic() +
    theme(
      text = element_text(family = "URWHelvetica", size = 8)
    )
)
library(cowplot)
library(dplyr)
library(tibble)
source("analysis/fit_data.R")

@@

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 0.1)
bounds <- rbind(
  bs_bnds, as_bnds
)

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 10, -5.5, -2)
)

# bring results together
bel_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

bel_model_fits

@@

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

@@

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 4.5, -8, -2.5)
)

# bring results together
bfi_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

bfi_model_fits

@@

CCDF plot is not right. Cant go back on its self which indicates there is probably some round off error somewhere throwing things off.

The individual fit isnt great and the Bs paramater is increasing up to the boundry, indicating it can only really take on a straight line / exponential fit. The parameters for the collective model are fairly central which raises questions as to why the fit is misbehaved in the tail.

@@

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-10, 5)
br_bnds <- c(1.0e-10, 5)
as_bnds <- c(1.0e-5, 5)
ar_bnds <- c(1.0e-10, 1.5)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

@@

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 105)
as_bnds <- c(1.0e-12, 0.1)
bounds <- rbind(
  bs_bnds, as_bnds
)

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 12, -8., -2.5)
)

# bring results together
blo_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

blo_model_fits

@@

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 500)
br_bnds <- c(1.0e-6, 500)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 1.5)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

@@

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 0.1)
bounds <- rbind(
  bs_bnds, as_bnds
)

@@

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 5.5, -6.5, -2.5)
)

# bring results together
bur_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

bur_model_fits

The only graph I can get to make sense is one where the collective reduces to the individual. The others show the ccdf going off.

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 100)
br_bnds <- c(1.0e-6, 100)
as_bnds <- c(1.0e-12, 10)
ar_bnds <- c(1.0e-12, 10)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 2)
as_bnds <- c(1.0e-12, 0.8)
bounds <- rbind(
  bs_bnds, as_bnds
)

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 2.5, -5, -1.5)
)

# bring results together
cad_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

cad_model_fits

Again, the likelihood scores look good but the model fits are doing crazy things at the tail!

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 10)
br_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 1.5)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 0.8)
bounds <- rbind(
  bs_bnds, as_bnds
)

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 2.7, -8., -2)
)

# bring results together
gil_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

gil_model_fits

Also has a weird CCDF plot

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 100)
br_bnds <- c(1.0e-6, 100)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 1.5)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 2)
bounds <- rbind(
  bs_bnds, as_bnds
)

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 5, -6.5, -1.5)
)

# bring results together
her_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

her_model_fits

Shit ccdf.

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 50)
br_bnds <- c(1.0e-6, 50)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 1.5)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.1)
bounds <- rbind(
  bs_bnds, as_bnds
)

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 6, -6.5, -2.5)
)

# bring results together
hhs_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

hhs_model_fits

Agin weird behaviour in the tail. Seems to be something to do with the Bs parameter approaching the lower bound. If the lower bound is made closer to zero (just 1e-7) the plot goes mad and the log-likelihood score becomes very large, indicating a round off error or something stupid.

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 10)
br_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 1.5)
bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.1)
bounds <- rbind(
  bs_bnds, as_bnds
)

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 4, -9, -2.5)
)

# bring results together
hor_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

hor_model_fits

Same problem as with the others.

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.1)
bounds <- rbind(
  bs_bnds, as_bnds
)

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 5, -6.5, -2.5)
)

# bring results together
mak_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

mak_model_fits

@@

Slight misbehaviour in the tail creaping up.

@@

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.1)
bounds <- rbind(
  bs_bnds, as_bnds
)

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 3.5, -7, -2.5)
)

# bring results together
mel_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

mel_model_fits

@@

Same problem with the tail.

@@

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.1)
bounds <- rbind(
  bs_bnds, as_bnds
)

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 4.5, -7.2, -2.5)
)

# bring results together
mpa_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

mpa_model_fits

@@

Same problem with the tail.

@@

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.1)
bounds <- rbind(
  bs_bnds, as_bnds
)

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 3., -5.5, -2.5)
)

# bring results together
rot_model_fits <- tibble(
  site = c(target_site, target_site),
  model = c("collective", "individual"),
  loglikelihood = c(
    colletive_result$solution$fmax, individual_result$solution$fmax
  ),
  p = c(colletive_result$solution$est[1], 1),
  k = c(
    length(colletive_result$solution$est),
    length(individual_result$solution$est)
  ),
  AIC = c(
    calc_aic(
      length(colletive_result$solution$est), colletive_result$solution$fmax
    ),
    calc_aic(
      length(individual_result$solution$est), individual_result$solution$fmax
    )
  )
)

rot_model_fits

@@

No problems here!

@@

# fit collective model
colletive_result <- fit_collective_model_to_data(data, bounds)

# view collective model likelihood space to check bounds look ok
colletive_result$llspace

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.1)
bounds <- rbind(
  bs_bnds, as_bnds
)

# make plot of model fits
make_full_plot(
  data$foraging_distance,
  list(
    "collective" = colletive_result$solution,
    "individual" = individual_result$solution
  ),
  subplot_coords = c(0.5, 3.5, -6.5, -2.5)
)

>>>>

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(ggplot2)
theme_set(
  theme_classic() +
    theme(
      text = element_text(family = "DejaVuSerif", size = 8)
    )
)
library(cowplot)
library(dplyr)
library(tibble)
source("analysis/fit_data.R")

library(showtext)
showtext_auto()

run_wagglefit_analysis <- function(
  target_site, data, collective_bounds, individual_bounds, subplot_coords
  ) {

  # run collective model
  colletive_result <- fit_collective_model_to_data(data, collective_bounds)

  # run individual model
  individual_result <- fit_individual_model_to_data(data, individual_bounds)

  # make plot of model fits
  full_plot <- make_full_plot(
    data$foraging_distance,
    list(
      "collective" = colletive_result$solution,
      "individual" = individual_result$solution
    ),
    subplot_coords = subplot_coords
  )

  # calculate ks statistics
  ks_test_result_collective <- calc_ks_boot(
    data$foraging_distance, colletive_result$solution$est, "collective"
  )
  ks_test_result_individual <- calc_ks_boot(
    data$foraging_distance, individual_result$solution$est, "individual"
  )

  # bring results together
  model_fits <- tibble(
    site = c(target_site, target_site),
    model = c("collective", "individual"),
    loglikelihood = c(
      colletive_result$solution$fmax, individual_result$solution$fmax
    ),
    p = c(colletive_result$solution$est[1], 1),
    bs = c(colletive_result$solution$est[2], individual_result$solution$est[1]),
    br = c(colletive_result$solution$est[3], NA),
    as = c(colletive_result$solution$est[4], individual_result$solution$est[2]),
    ar = c(colletive_result$solution$est[5], NA),
    k = c(
      length(colletive_result$solution$est),
      length(individual_result$solution$est)
    ),
    AIC = c(
      calc_aic(
        length(colletive_result$solution$est), colletive_result$solution$fmax
      ),
      calc_aic(
        length(individual_result$solution$est), individual_result$solution$fmax
      )
    ),
    ks_statistic = c(
      ks_test_result_collective$ks$statistic[[1]],
      ks_test_result_individual$ks$statistic[[1]]
    ),
    ks_pvalue = c(
      ks_test_result_collective$ks.boot.pvalue,
      ks_test_result_individual$ks.boot.pvalue
    )
  )

  return(
    list(
      fit_result = model_fits, fit = full_plot,
      individual_llspace = individual_result$llspace,
      collective_llspace = colletive_result$llspace
    )
  )
}

all_sites <- as.list(rep(0, 20))
names(all_sites) <- get_data() %>%
    select(site) %>%
    unique() %>%
    pull()

@@

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 10)
br_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 0.5)
collective_bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 0.1)
individual_bounds <- rbind(
  bs_bnds, as_bnds
)

# set coordinates for histogram subplot
subplot_coords <- c(0.5, 10, -5.5, -2)

all_sites[[target_site]] <- run_wagglefit_analysis(
  target_site, data, collective_bounds, individual_bounds, subplot_coords
)

all_sites[[target_site]]

all_sites[[target_site]]$fit

@@

@@

# set coordinates for histogram subplot
subplot_coords <- c(0.5, 4.5, -6.5, -2.5)

all_sites[[target_site]] <- run_wagglefit_analysis(
  target_site, data, collective_bounds, individual_bounds, subplot_coords
)

all_sites[[target_site]]

all_sites[[target_site]]$fit

@@

The individual fit isnt great and the Bs paramater is increasing up to the boundry, indicating it can only really take on a straight line / exponential fit. The parameters for the collective model are fairly central in the likelihood space, the fit looks very good.

@@

@@

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-10, 5)
br_bnds <- c(1.0e-10, 5)
as_bnds <- c(1.0e-5, 5)
ar_bnds <- c(1.0e-10, 1.5)
collective_bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 5505)
as_bnds <- c(1.0e-12, 0.1)
individual_bounds <- rbind(
  bs_bnds, as_bnds
)

# set coordinates for histogram subplot
subplot_coords <- c(0.5, 12, -8., -2.5)

all_sites[[target_site]] <- run_wagglefit_analysis(
  target_site, data, collective_bounds, individual_bounds, subplot_coords
)

all_sites[[target_site]]

all_sites[[target_site]]$fit

@@

@@

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 500)
br_bnds <- c(1.0e-6, 500)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 1.5)
collective_bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 0.1)
individual_bounds <- rbind(
  bs_bnds, as_bnds
)

# set coordinates for histogram subplot
subplot_coords <- c(0.5, 5.5, -6.5, -2.5)

all_sites[[target_site]] <- run_wagglefit_analysis(
  target_site, data, collective_bounds, individual_bounds, subplot_coords
)

all_sites[[target_site]]

all_sites[[target_site]]$fit

The collective model roughly follows the individual model but is able to acheive a slightly improved fit to the shoulder, hence it provides a higher likelihood score. The AIC indicates this is overfitting, suggesting the individual model provides a more parsimonious explanation.

$p$ does not approach 1 as one might expect, indicating there is overfitting and so a comparison with an individual model is required.

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 10)
br_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 10)
ar_bnds <- c(1.0e-12, 10)
collective_bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 2)
as_bnds <- c(1.0e-12, 0.8)
individual_bounds <- rbind(
  bs_bnds, as_bnds
)

# set coordinates for histogram subplot
subplot_coords <- c(0.5, 2.5, -5, -1.5)

all_sites[[target_site]] <- run_wagglefit_analysis(
  target_site, data, collective_bounds, individual_bounds, subplot_coords
)

all_sites[[target_site]]

all_sites[[target_site]]$fit

The collective model provides the most parsimonious and best fit.

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 10)
br_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 1.5)
collective_bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 0.8)
individual_bounds <- rbind(
  bs_bnds, as_bnds
)

# set coordinates for histogram subplot
subplot_coords <- c(0.5, 2.7, -8., -2)

all_sites[[target_site]] <- run_wagglefit_analysis(
  target_site, data, collective_bounds, individual_bounds, subplot_coords
)

all_sites[[target_site]]

all_sites[[target_site]]$fit

The collective model provides the best fit to the data, but the proportion of scouts is high.

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 100)
br_bnds <- c(1.0e-6, 100)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 1.5)
collective_bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 2)
individual_bounds <- rbind(
  bs_bnds, as_bnds
)

# set coordinates for histogram subplot
subplot_coords <- c(0.5, 5, -6.5, -1.5)

all_sites[[target_site]] <- run_wagglefit_analysis(
  target_site, data, collective_bounds, individual_bounds, subplot_coords
)

all_sites[[target_site]]

all_sites[[target_site]]$fit

Collective model provides the best fit but falls under the tail and shoulder. The individual model strugles to find a good fit, probably due to the tail.

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 50)
br_bnds <- c(1.0e-6, 50)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 1.5)
collective_bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.1)
individual_bounds <- rbind(
  bs_bnds, as_bnds
)

# set coordinates for histogram subplot
subplot_coords <- c(0.5, 6, -6.5, -2.5)

all_sites[[target_site]] <- run_wagglefit_analysis(
  target_site, data, collective_bounds, individual_bounds, subplot_coords
)

all_sites[[target_site]]

all_sites[[target_site]]$fit

Collective model provides a very good fit, whilst the individual model fails to find much traction. The proportion of scouts goes very low (~3%) suggesting the majority of the colony are following a small number of scouting individuals.

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 10)
br_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 1.5)
collective_bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.1)
individual_bounds <- rbind(
  bs_bnds, as_bnds
)

# set coordinates for histogram subplot
subplot_coords <- c(0.5, 4, -9, -2.5)

all_sites[[target_site]] <- run_wagglefit_analysis(
  target_site, data, collective_bounds, individual_bounds, subplot_coords
)

all_sites[[target_site]]

all_sites[[target_site]]$fit

Again the collective model provides a good fit to the data, however, the individual model fits poorly, reducing to an exponential.

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 10)
br_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 0.5)
collective_bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 20)
as_bnds <- c(1.0e-12, 1.1)
individual_bounds <- rbind(
  bs_bnds, as_bnds
)

@@

# set coordinates for histogram subplot
subplot_coords <- c(0.5, 5, -6.5, -2.5)

all_sites[[target_site]] <- run_wagglefit_analysis(
  target_site, data, collective_bounds, individual_bounds, subplot_coords
)

all_sites[[target_site]]

all_sites[[target_site]]$fit

@@

Collective model provides the best fit, however it misses a large section of the shoulder for the tail. The $bs$ parameter wants to go to zero, however when let go bellow 1e-6 the behaviour becomes very erratic and the fit deteriorates.

@@

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 10)
br_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 0.5)
collective_bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.1)
individual_bounds <- rbind(
  bs_bnds, as_bnds
)

# set coordinates for histogram subplot
subplot_coords <- c(0.5, 3.5, -7, -2.5)

all_sites[[target_site]] <- run_wagglefit_analysis(
  target_site, data, collective_bounds, individual_bounds, subplot_coords
)

all_sites[[target_site]]

all_sites[[target_site]]$fit

@@

Collective provides the best fit.

@@

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 10)
br_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 0.5)
collective_bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.1)
individual_bounds <- rbind(
  bs_bnds, as_bnds
)

# set coordinates for histogram subplot
subplot_coords <- c(0.5, 4.5, -7.2, -2.5)

all_sites[[target_site]] <- run_wagglefit_analysis(
  target_site, data, collective_bounds, individual_bounds, subplot_coords
)

all_sites[[target_site]]

all_sites[[target_site]]$fit

@@

Colletive provides the best fit.

@@

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 10)
br_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 0.5)
collective_bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.1)
individual_bounds <- rbind(
  bs_bnds, as_bnds
)

# set coordinates for histogram subplot
subplot_coords <- c(0.5, 3., -5.5, -2.5)

all_sites[[target_site]] <- run_wagglefit_analysis(
  target_site, data, collective_bounds, individual_bounds, subplot_coords
)

all_sites[[target_site]]

all_sites[[target_site]]$fit

@@

Collective provides the best fit.

@@

# set up bounds for the collective model
p_bnds <- c(0, 1.0)
bs_bnds <- c(1.0e-6, 10)
br_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.5)
ar_bnds <- c(1.0e-12, 0.5)
collective_bounds <- rbind(
  p_bnds, bs_bnds,
  br_bnds, as_bnds,
  ar_bnds
)

# set up bounds for the individual model
bs_bnds <- c(1.0e-6, 10)
as_bnds <- c(1.0e-12, 1.1)
individual_bounds <- rbind(
  bs_bnds, as_bnds
)

# set coordinates for histogram subplot
subplot_coords <- c(0.5, 3.5, -6.5, -2.5)

all_sites[[target_site]] <- run_wagglefit_analysis(
  target_site, data, collective_bounds, individual_bounds, subplot_coords
)

all_sites[[target_site]]

all_sites[[target_site]]$fit
